Joshua 2.0: An Open Source Toolkit for Machine Translation \\with Syntax, Semirings and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
add semiring parsing
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1608 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\author{
Zhifei Li,\,\,\,
Chris Callison-Burch,\,\,\,
%Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\,
Ann Irvine,\,\,\, 
%Sanjeev Khudanpur,\,\,\,
Lane Schwartz,$^\star$\,\,\, 
\\ {\bf
Wren N.\,G.\,Thornton,\,\,\,
Ziyuan Wang,\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
%$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\section{Semiring Parsing}
\todo{zhifei}

\cite{li-eisner:2009:EMNLP}

\section{Discriminative Training}
\todo{zhifei}

>>>>

\author{
Zhifei Li,\,\,\,
Chris Callison-Burch,\,\,\,
Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\,
\\ {\bf
Ann Irvine,\,\,\,  
Sanjeev Khudanpur,\,\,\,
Lane Schwartz,$^\star$\,\,\, 
Wren N.\,G.\,Thornton,\,\,\,}
\\ {\bf
Ziyuan Wang,\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan
}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\section{Semiring Parsing}

In \joshua, we use a {\em hypergraph} (or {\em packed forest}) to compactly 
represent the exponentially many derivation trees generated by the decoder for a 
particular foreign input sentence.
Given a hypergraph, we may perform many atomic inference operations
such as finding one-best, $k$-best, or expectations over the hypergraph.
To perform each operation, we may implement a dedicated dynamic programming algorithm.
However, a more general framework to specify these algorithms is semiring-weighted parsing \cite{semiringparsing}.
Within this framework, we implemented all the algorithms (i.e.,
inside, outside, and inside-outside speedup) described by \newcite{li-eisner:2009:EMNLP},
and also the first-order expectation semiring \cite{eisner-expectation-semiring} and its
second-order version \cite{li-eisner:2009:EMNLP}.

% The original first-order expectation semiring allows us to efficiently
% compute a vector of first-order statistics (expectations; first
% derivatives) on the set of paths in a lattice or the set of trees in a
% hypergraph.  The second-order expectation semiring {\em additionally} computes
% a matrix of second-order statistics (expectations of {\em products}; second
% derivatives (Hessian); derivatives of expectations).

%% use of expectation and variance semiring
The first- and second-order expectation semirings can be used compute many interesting quantities over the hypergraph.
These quantities include expected hypothesis length, feature expectation, entropy, cross-entropy, Kullback-Leibler divergence,
Bayes risk, variance of hypothesis length, gradient of entropy and Bayes risk, covariance and Hessian matrix, and so on.
% The second-order expectation semiring is essential for many interesting training paradigms 
% such as deterministic annealing \cite{Rose98deterministicannealing}, minimum risk \cite{smith-eisner:2006:POS},
% active and semi-supervised learning \cite{entropy-mini,semiCRF-jiao}.
% In these settings, we must compute the gradient of entropy or risk. 
% The semiring can also be used for second-order gradient optimization algorithms.

\section{Hypergraph-based Discriminative Training}
\todo{zhifei}
